\documentclass{article}
\usepackage{geometry}
\geometry{
	a4paper,
	left = 20mm,
	right = 20mm,
	top = 30mm
}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{flushleft}
	\textbf{Mayank Sharma}\\
	Department of Computer Science and Engineering\\
	Indian 	Institute of Technology Kanpur, India\\
	\textit{Email:  msharma@iitk.ac.in}\\
	\hfill\\
	\hrule
	\vspace{0.8mm}
	\hrule
	\hfill\\
	\vspace{0.8mm}
	I am Mayank Sharma. I am pursuing Computer Science and Engineering from Indian Institute of Technology, Kanpur. During my schooling years, I used to open my laptop and PCs and used to fiddle with its parts. Hence, I developed a deep interest towards computer and Software Engineering in general.
	I am pursuing so and so projects presently.
	I carry a positive attitude towards life and I'm optimistics about situations. In my free time, I love listening to music (particularly Pink Floyd, Zara Larsson and Queen) and I go to gym as regularly as I can. I have also lost 20 kgs of weight during my freshman year.
	\vspace{3mm}
	\hfill\\
	\hrule
	\vspace{0.8mm}
	\hrule
	\hfill\\
	\textbf{Education}\\
	\hfill\\
	\begin{tabular}{|l|l|l|l|}
		\hline
		BTech & 2020 & Indian Institute of Technology, Kanpur & 6.6\\
		\hline
		Matriculation & 2014 & Central Academy Sr. Sec. School, Chittorgarh & 10.0\\
		\hline
		Intermediate & 2016 & Children Sr. Sec. School, Dadabari, Kota & 92.0 \%\\
		\hline
	\end{tabular}
	\hfill\\
	\hfill\\
	\hfill\\
	\textbf{Course details}\\
	\hfill\\
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Semester} & \textbf{Total credits} & \textbf{Highlights}\\
		\hline
		Aug 2016 - Dec 2016 & 50 & ESC-101\\
		\hline
		Jan 2017 - April 2016 & 48 & PHY103, MTH102\\
		\hline
		Aug 2017 - Dec 2017 & 50 & ESC - 201, CS201, CS203\\
		\hline
		Jan 2018 - April 2018 & 56 & ESO207, MSO201\\
		\hline
	\end{tabular}
	\hfill\\
	\hfill\\
	\hfill\\
	\textbf{Skills}\\
	\hfill\\
	\begin{tabular}{ l c l }
		Computer Science & : & Operating Systems, Data Science \& Machine Learning\\
		Programming languages & : &C++, Python, C, Javascript and Typescript, \\ &&Bash Scripting, MATLAB
	\end{tabular}
	\hfill\\
	\hfill\\
	\textbf{Projects}\\
	\begin{enumerate}
		\item Robocon 2018, Member
		\item Linux from Scratch under Association of Computing Activities (ACA)
		\item The Automatic Stamper, TA201 project 
	\end{enumerate}
	\hfill\\
	\textbf{Awards and achievements}\\
	\renewcommand{\labelitemi}{\textendash}
	\begin{itemize}
		\item[-] JEE Advanced 2016, Rank 630 among 200 thousand selected candidates.
		\item[-] JEE Mains 2016, Rank 2237 among 1.2 million candidates.
		\item[-] KVPY Fellowship Award awarded by Department of Science and Technology, India.
		\item[-] National Science Talent Search Examination among 3.2+ Lakh applicants.
	\end{itemize}
	\hfill\\
	\textbf{Hobbies}\\
	\begin{itemize}
		\item[-] Sports: Basketball \& Badminton 
		\item[-] Going to Gym, Listening to Music  
	\end{itemize}
\end{flushleft}
\end{document}


